The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-04 analysis/paper/paper.qmd

The `tf-idf` statistic shows high values for the names of thesis locations that tend to be high-frequency thesis-specific words. As such, it shows words that are the most important to one document in a collection of documents [@silge2017].

>>>>

### Word embeddings

[Describe word embeddings ...]

```{r word-embeddings-pmi}
#| include: false

# To what extent do words co-occur with other words?
tidy_pmi <- get_pmi(emu_theses, title_col = "title", text_col = "text_clean")

The high-dimensional sparse matrix of word features is projected into reduced, 100-dimensional set of features.

```{r word-embeddings-svd}

# Determine word vectors using SVD, a method for dimensionality reduction
tidy_word_vectors <- tidy_pmi |> 
  widely_svd(
    item1, item2, pmi,
    nv = 100, maxit = 1000
  )

[What terms should be checked with the function below?]

```{r word-embeddings-nn}

# Calculate nearest neighbours of a given word
tidy_word_vectors |> 
  nearest_neighbors("resilience")

The first [?] components... [what do they show?]

```{r word-embeddings}

# The first n components with top words found in the corpus of theses
visualise_first_n_components(tidy_word_vectors, 24, 12)

```{r word-embeddings}

# Summarise word embeddings into document embeddings for modeling purposes
word_matrix <- tidy_emu_theses |> 
  count(title, word) |> 
  cast_sparse(title, word, n)

embedding_matrix <- tidy_word_vectors |> 
  cast_sparse(item1, dimension, value)

doc_matrix <- word_matrix %*% embedding_matrix

dim(doc_matrix)

doc_matrix
